\bf Tearing Mode Dynamics in Tokamak Plasmas

### 2021-11-28 Documentation/TearingModeTheory.tex
Latest version
Started isolated islands

Equation~(\ref{e509}) yields 
\begin{equation}\label{e513}
{\cal J}_0({\mit\Omega},\zeta,T)= 
\frac{1}{2}\,d_{\mit\Omega}\!\left[M\left(M+\frac{L}{1+\tau}\right)\right]\!\widetilde{X}^2 + \overline{\cal J}_0({\mit\Omega},T),
\end{equation}
where $\overline{{\cal J}}_0({\mit\Omega},T)$ is an undetermined flux-surface function.

\subsection{Fluid Velocities}\label{s8.6}
The flux-surface functions $M({\mit\Omega},T)$ and $L({\mit\Omega},T)$ are directly related to the lowest-order perpendicular
velocities of the various fluid species in the island rest frame. In fact, as is clear from Sections~\ref{s4.2}, \ref{s4.3}, and \ref{s8.2}, 
\begin{align}
V_\theta(x,\zeta,T) &= -\frac{r_s\,\omega_\ast}{m}\,|X|\,M({\mit\Omega},T),\\[0.5ex]
V_{\theta\,i}(x,\zeta,T)& = -\frac{r_s\,\omega_\ast}{m}\,|X|\,Y_i({\mit\Omega},T)\\[0.5ex]
V_{\theta\,e}(x,\zeta,T)& = -\frac{r_s\,\omega_\ast}{m}\,|X|\,Y_e({\mit\Omega},T),
\end{align}
where
\begin{align}
Y_i({\mit\Omega},T)&= M+\left(\frac{1}{1+\tau}\right)L,\label{e518}\\[0.5ex]
Y_e({\mit\Omega},T)&= Y_i- L.
\end{align}
Here, $V_\theta$, $V_{\theta\,i}$, and $V_{\theta\,e}$ refer to velocity components of the MHD, ion, and
electron fluid, respectively. Note that $Y_i$ and $Y_e$ are both zero inside the magnetic separatrix of the island chain.

@@

\subsection{Higher-Order Solution}
We need to evaluate Equation~(\ref{e469}) to third order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
we obtain
\begin{equation}\label{e514}
\frac{d(\ln \hat{w}^{\,2})}{dT}\,\cos\zeta = \{F_e, {\mit\Omega}\} + \epsilon_\beta\,\epsilon_d\,\epsilon_\eta\,{\cal J}_0,
\end{equation}
where
\begin{equation}
F_e({\mit\Omega},\zeta,T)= \epsilon_d^2\,({\mit\Phi}_2+\epsilon_d\,{\mit\Phi}_3)-\epsilon_d^{\,2}\left(\frac{\tau}{1+\tau}\right)({\cal N}_2+\epsilon_d\,{\cal N}_3)
- \epsilon_d^2\,s\,Y_e({\mit\Psi}_2+\epsilon_d\,{\mit\Psi}_3),
\end{equation}
and use has been made of Equations~(\ref{e429})--(\ref{e431}), (\ref{e500}), (\ref{e501}), (\ref{e503}), and (\ref{e505}). 
The flux-surface average of Equation~(\ref{e514}) yields
\begin{equation}
\overline{\cal J}_0({\mit\Omega},T) = \frac{1}{\epsilon_\beta\,\epsilon_d\,\epsilon_\eta}\frac{d(\ln \hat{w}^{\,2})}{dT}\,\frac{\langle\cos\zeta\rangle}{\langle 1\rangle},
\end{equation}
where use has been made of Equations~(\ref{e5111}), (\ref{e512}), and (\ref{e513}). Hence, we
can write
\begin{equation}\label{e524a}
{\cal J}_0({\mit\Omega},\zeta)= 
\frac{1}{2}\,d_{\mit\Omega}\!\left(M\,Y_i\right)\widetilde{X}^2+ \frac{1}{\epsilon_\beta\,\epsilon_d\,\epsilon_\eta}\frac{d(\ln \hat{w}^{\,2})}{dT}\,\frac{\langle\cos\zeta\rangle}{\langle 1\rangle},
\end{equation}
where use has been made of Equation~(\ref{e518}). 
The first term on the right-hand side of the previous equation represents the parallel return current driven by the perpendicular {\em polarization current}\/ associated with the
acceleration of the ion fluid around the magnetic separatrix of the island chain (Smolyakov 1993; Smolyakov, et al.\ 1995). 
In fact, it is easily seen that if the ion fluid could pass freely through the separatrix (i.e., ${\mit\Phi}_0\propto X$ and ${\cal N}_0\propto X$) then the term in question would be zero. The second term on the right-hand side of the previous equation represents the parallel current driven
inductively when the reconnected flux at the resonant surfaces varies in time.

We need to evaluate Equation~(\ref{e471}) to first order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
we obtain
\begin{equation}
0= \epsilon_d\,\{{\cal V}_1, {\mit\Omega}\} + \epsilon_D\,(X^2\,d_{\mit\Omega} L + L),
\end{equation}
where use has been made of Equations~(\ref{e498}), (\ref{e500}),  and (\ref{e501}). The flux-surface average of the
previous equation yields
\begin{equation}
\langle X^2\rangle\,d_{\mit\Omega} L +\langle 1\rangle\,L = 0,
\end{equation}
where use has been made of Equation~(\ref{e5111}). 
We can solve the previous equation, subject to the boundary condition (\ref{e502}), to give
\begin{equation}\label{e526}
L({\mit\Omega})=\left\{
\begin{array}{llr}
0&&-1\leq {\mit\Omega}\leq 1\\[0.5ex]
1/\langle X^2\rangle&~~&{\mit\Omega}>1
\end{array}\right..
\end{equation}
Here, we have taken into account the previously mentioned fact that $L=0$ within the island separatrix.
Note that $L$ is discontinuous across the island separatrix, which implies that the density gradient, and, hence,
the diamagnetic velocity, are both also discontinuous across the separatrix. Of course, there is not a real
discontinuity. Given that the discontinuity in $L$ is mandated by the ordering $\epsilon_d=(\rho_\beta/w)^2\ll 1$, which
requires $L$ to be a flux-surface function, and, hence, zero by symmetry inside the separatrix, it follows that the discontinuity is resolved by a thin layer of characteristic thickness $\rho_\beta$ on the island
separatrix.

We need to evaluate Equation~(\ref{e470}) to first order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
we obtain
\begin{equation}\label{e528a}
0 =\epsilon_d\,\{{\cal J}_1,{\mit\Omega}\} +\epsilon_\chi\,X\,d_{{\mit\Omega}}\!\left[d_{\mit\Omega}\!\left(X^3\,d_{\mit\Omega} Y_i\right)\right].
\end{equation}
where use has been made of Equations~(\ref{e498}), (\ref{e500}), (\ref{e501}), (\ref{e503}), (\ref{e505}), and (\ref{e518}). The flux-surface average of the previous equation yields 
\begin{equation}
d_{\mit\Omega}^{\,2}\!\left(\langle X^4\rangle\,d_{\mit\Omega} Y_i\right)= 0.
\end{equation}
We can solve the previous equation, subject to the boundary conditions (\ref{e502}) and (\ref{e506}), to give
\begin{equation}\label{e530}
Y_i({\mit\Omega},T)=\frac{v'(T)}{\int_1^\infty \!\frac{d{\mit\Omega}}{\langle X^4\rangle}}\left\{
\begin{array}{llr}
0&&-1\leq {\mit\Omega}\leq 1\\[0.5ex]
\int_1^{\mit\Omega}\! \frac{d{\mit\Omega}'}{\langle X^4\rangle}&~~&{\mit\Omega}>1
\end{array}\right.
\end{equation}
(Fitzpatrick \& Waelbroeck 2005).
Here, we have rejected, as unphysical, the solution that blows up as ${\mit\Omega}^{\,1/2}$ as ${\mit\Omega}\rightarrow\infty$. 
We have also made use of the fact that $Y_i=0$ within the magnetic separatrix of the island chain. Finally, we have  demanded that the ion
fluid velocity, and, hence, the function $Y_i$,  be continuous across the separatrix, because the ion fluid possesses finite perpendicular viscosity. 
Note, however, that the discontinuity in the function $L({\mit\Omega})$ across the separatrix [see Equation~(\ref{e526})] implies that the
MHD and electron fluid velocities are  discontinuous across the separatrix. (See Section~\ref{s8.6}.) As previously
mentioned, these discontinuities are resolved in a layer of characteristic thickness $\rho_\beta$.

We need to evaluate Equation~(\ref{e472}) to second order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
we obtain
\begin{equation}
0=\epsilon_d\,\{{\cal V}_1,{\mit\Omega}\} + \epsilon_\chi\,(X^2\,d_{\mit\Omega} {\cal V}_{(0)} + {\cal V}_{(0)}),
\end{equation}
where use has been made of Equations~(\ref{e498}) and (\ref{e508}). The flux-surface average of the
previous equation yields
\begin{equation}
\langle X^2\rangle\,d_{\mit\Omega} {\cal V}_{(0)} +\langle 1\rangle \,{\cal V}_{(0)}= 0.
\end{equation}
 This equation can be solved, subject to the boundary condition (\ref{e486a}) to
give
\begin{equation}
{\cal V}_{(0)}({\mit\Omega}, T) = 0.
\end{equation}
Hence, we conclude that the lowest-order ion parallel flow is unaffected by the presence of the island chain.

@@

Equations~(\ref{e528a}) and (\ref{e543}) can be combined to give (Fitzpatrick \& Waelbroeck 2005)
\begin{align}
{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) &=\frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\int_1^\infty
\left\langle X^{2}\,d_{\mit\Omega}\!\left[d_{\mit\Omega}(X^3\,d_{\mit\Omega}Y_i)\right]\right\rangle d{\mit\Omega}\nonumber\\[0.5ex]
&=\frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\int_1^\infty d_{\mit\Omega}\!\left(-\langle X\rangle\,Y_i
+2\,\langle X^3\rangle\,d_{\mit\Omega} Y_i + \langle X^5\rangle\,d_{\mit\Omega}^{\,2} Y_i\right)d{\mit\Omega}\nonumber\\[0.5ex]
&= \frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\,\lim_{\mit\Omega\rightarrow\infty}\left(-\langle X\rangle\,Y_i
+2\,\langle X^3\rangle\,d_{\mit\Omega} Y_i + \langle X^5\rangle\,d_{\mit\Omega}^{\,2} Y_i\right),
\end{align}
where use has been made of the facts that $Y_i$ is zero inside the island separatrix, and $Y_i$ is continuous across the separatrix.
Combining the previous equation with Equation~(\ref{e530}), we obtain (Fitzpatrick \& Waelbroeck 2005)
\begin{equation}\label{e545}
{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)  =- \frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi\,v'}{\hat{w}}.
\end{equation}
The previous equation yields
\begin{equation}
\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}} = \left(\frac{\tau_\varphi\,\hat{w}^{\,4}}{2\,\tau_H^{\,2}}{\rm Im}\!\right)\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right),
\end{equation}
where use has been made of Equation~(\ref{e489}). The same relation can be obtained by integrating Equation~(\ref{e182}) across the resonant surface, making use of Equation~(\ref{e157}), as well as the
identification
\begin{equation}
\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}} = m\left[r\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right]_{r_{s-}}^{r_{s+}}.
\end{equation}
The latter result merely states that the  discontinuity in the MHD fluid velocity gradient that develop at the resonant
surface is mirrored by an equal discontinuity in the ion fluid velocity gradient (because the discontinuity is ultimately due to 
a discontinuity in the ${\bf E}\times {\bf B}$ velocity gradient).

@@

\section{Isolated Magnetic Island Chain}
\subsection{Introduction}
Suppose that the wall surrounding the plasma is perfectly conducting (i.e.\, $\tau_w\rightarrow\infty$), and that there is no current
flowing through the external magnetic-field coil (i.e., $\hat{I}_c=0$). In this case, assuming that $d/dt = -{\rm i}\,\omega$, Equations~(\ref{e202}), 
(\ref{e203}), and (\ref{epw}),  yield 
\begin{equation}\label{e563}
\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) ={\mit\Delta}_{pw},
\end{equation}
where ${\mit\Delta}_{pw}$ is the (real) perfect-wall tearing stability index.

\subsection{Rutherford Island Width Evolution Equation}
It is clear from the previous equation that
\begin{equation}
{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) = 0,
\end{equation}
which implies that no electromagnetic torque is exerted at the resonant surface. (See Section~\ref{storque}.) 
Hence, Equations~(\ref{e559}) and (\ref{e563}) yield the {\em Rutherford island width evolution equation}\/ (Rutherford 1973):
\begin{equation}
I_2\,\tau_R\,\frac{d}{dt}\!\left(\frac{4\,w}{r_s}\right)= {\mit\Delta}_{nw}.
\end{equation}
According to this equation, if the perfect-wall tearing stability index is positive then the width of the magnetic
island chain at the resonant surface grows algebraically on the resistive evolution timescale, $\tau_R$.

>>>>

Equation~(\ref{e509}) yields 
\begin{equation}\label{e513}
{\cal J}_0({\mit\Omega},\zeta,T)= 
\frac{1}{2}\,d_{\mit\Omega}\!\left[M\left(M+\frac{L}{1+\tau}\right)\right]\!\widetilde{X^2} + \overline{\cal J}_0({\mit\Omega},T),
\end{equation}
where $\overline{{\cal J}}_0({\mit\Omega},T)$ is an undetermined flux-surface function.

\subsection{Fluid Velocities}\label{s8.6}
The flux-surface functions $M({\mit\Omega},T)$ and $L({\mit\Omega},T)$ are directly related to the lowest-order perpendicular
velocities of the various fluid species in the island rest frame. In fact, as is clear from Sections~\ref{s4.2}, \ref{s4.3}, and \ref{s8.2}, 
\begin{align}
V_{\theta\,e}(X,\zeta,T)& = -\frac{r_s\,\omega_\ast}{m}\,|X|\,Y_e({\mit\Omega},T),\\[0.5ex]
V_\theta(X,\zeta,T) &= -\frac{r_s\,\omega_\ast}{m}\,|X|\,M({\mit\Omega},T),\\[0.5ex]
V_{\theta\,i}(X,\zeta,T)& = -\frac{r_s\,\omega_\ast}{m}\,|X|\,Y_i({\mit\Omega},T),
\end{align}
where
\begin{align}
Y_e({\mit\Omega},T)&= M- \left(\frac{\tau}{1+\tau}\right)L,\\[0.5ex]
Y_i({\mit\Omega},T)&= M+\left(\frac{1}{1+\tau}\right)L,\label{e518}
\end{align}
Here,  $V_{\theta\,e}$, $V_\theta$, and $V_{\theta\,i}$  refer to velocity components of the electron, MHD, and ion 
 fluid, respectively. Note that $Y_e$ and $Y_i$ are both zero inside the magnetic separatrix of the island chain.

@@

\subsection{Higher-Order Solution}
We need to evaluate Equation~(\ref{e469}) to third order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
we obtain
\begin{equation}\label{e514}
\frac{d(\ln \hat{w}^{\,2})}{dT}\,\cos\zeta = \{F_e, {\mit\Omega}\} + \epsilon_\beta\,\epsilon_d\,\epsilon_\eta\,{\cal J}_0,
\end{equation}
where
\begin{equation}
F_e({\mit\Omega},\zeta,T)= \epsilon_d^2\,({\mit\Phi}_2+\epsilon_d\,{\mit\Phi}_3)-\epsilon_d^{2}\left(\frac{\tau}{1+\tau}\right)({\cal N}_2+\epsilon_d\,{\cal N}_3)
- \epsilon_d^2\,s\,Y_e({\mit\Psi}_2+\epsilon_d\,{\mit\Psi}_3),
\end{equation}
and use has been made of Equations~(\ref{e429})--(\ref{e431}), (\ref{e500}), (\ref{e501}), (\ref{e503}), and (\ref{e505}). 
The flux-surface average of Equation~(\ref{e514}) yields
\begin{equation}
\overline{\cal J}_0({\mit\Omega},T) = \frac{1}{\epsilon_\beta\,\epsilon_d\,\epsilon_\eta}\frac{d(\ln \hat{w}^{2})}{dT}\,\frac{\langle\cos\zeta\rangle}{\langle 1\rangle},
\end{equation}
where use has been made of Equations~(\ref{e5111}), (\ref{e512}), and (\ref{e513}). Hence, we
can write
\begin{equation}\label{e524a}
{\cal J}_0({\mit\Omega},\zeta)= 
\frac{1}{2}\,d_{\mit\Omega}\!\left(M\,Y_i\right)\widetilde{X^2}+ \frac{1}{\epsilon_\beta\,\epsilon_d\,\epsilon_\eta}\frac{d(\ln \hat{w}^{2})}{dT}\,\frac{\langle\cos\zeta\rangle}{\langle 1\rangle},
\end{equation}
where use has been made of Equation~(\ref{e518}). 
The first term on the right-hand side of the previous equation represents the parallel return current driven by the perpendicular {\em polarization current}\/ associated with the
acceleration of the ion fluid around the magnetic separatrix of the island chain (Smolyakov 1993; Smolyakov, et al.\ 1995). 
In fact, it is easily seen that if the ion fluid could pass freely through the separatrix (i.e., ${\mit\Phi}_0\propto X$ and ${\cal N}_0\propto X$) then the term in question would be zero. The second term on the right-hand side of the previous equation represents the parallel current driven
inductively when the reconnected flux at the resonant surfaces varies in time.

We need to evaluate Equation~(\ref{e471}) to first order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
we obtain
\begin{equation}
0= \epsilon_d\,\{{\cal V}_1, {\mit\Omega}\} + \epsilon_D\,(X^2\,d_{\mit\Omega} L + L),
\end{equation}
where use has been made of Equations~(\ref{e498}), (\ref{e500}),  and (\ref{e501}). The flux-surface average of the
previous equation yields
\begin{equation}
\langle X^2\rangle\,d_{\mit\Omega} L +\langle 1\rangle\,L = 0,
\end{equation}
where use has been made of Equation~(\ref{e5111}). 
We can solve the previous equation, subject to the boundary condition (\ref{e502}), to give
\begin{equation}\label{e526}
L({\mit\Omega})=\left\{
\begin{array}{llr}
0&&-1\leq {\mit\Omega}\leq 1\\[0.5ex]
1/\langle X^2\rangle&~~&{\mit\Omega}>1
\end{array}\right..
\end{equation}
Here, we have taken into account the previously mentioned fact that $L=0$ within the island separatrix.
Note that $L$ is discontinuous across the island separatrix, which implies that the density gradient---and, hence,
the diamagnetic velocity---are both also discontinuous across the separatrix. Of course, there is not a real
discontinuity. Given that the discontinuity in $L$ is mandated by the ordering $\epsilon_d=(\rho_\beta/w)^2\ll 1$, which
requires $L$ to be a flux-surface function---and, hence, zero, by symmetry, inside the separatrix---it is plausible that the discontinuity is resolved by a thin layer of characteristic thickness $\rho_\beta$ on the island
separatrix.

We need to evaluate Equation~(\ref{e470}) to first order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
we obtain
\begin{equation}\label{e528a}
0 =\epsilon_d\,\{{\cal J}_1,{\mit\Omega}\} +\epsilon_\chi\,X\,d_{{\mit\Omega}}\!\left[d_{\mit\Omega}\!\left(X^3\,d_{\mit\Omega} Y_i\right)\right].
\end{equation}
where use has been made of Equations~(\ref{e498}), (\ref{e500}), (\ref{e501}), (\ref{e503}), (\ref{e505}), and (\ref{e518}). The flux-surface average of the previous equation yields 
\begin{equation}
d_{\mit\Omega}^{\,2}\!\left(\langle X^4\rangle\,d_{\mit\Omega} Y_i\right)= 0.
\end{equation}
We can solve the previous equation, subject to the boundary conditions (\ref{e502}) and (\ref{e506}), to give
\begin{equation}\label{e530}
Y_i({\mit\Omega},T)=\frac{v'(T)}{\int_1^\infty \!\frac{d{\mit\Omega}}{\langle X^4\rangle}}\left\{
\begin{array}{llr}
0&&-1\leq {\mit\Omega}\leq 1\\[0.5ex]
\int_1^{\mit\Omega}\! \frac{d{\mit\Omega}'}{\langle X^4\rangle}&~~&{\mit\Omega}>1
\end{array}\right.
\end{equation}
(Fitzpatrick \& Waelbroeck 2005).
Here, we have rejected, as unphysical, the solution that blows up as ${\mit\Omega}^{\,1/2}$ as ${\mit\Omega}\rightarrow\infty$. 
We have also made use of the fact that $Y_i=0$ within the magnetic separatrix of the island chain. Finally, we have  demanded that the ion
fluid velocity---and, hence, the function $Y_i$---is continuous across the separatrix, because the ion fluid possesses finite perpendicular viscosity. 
Note, however, that the discontinuity in the function $L({\mit\Omega})$ across the separatrix [see Equation~(\ref{e526})] implies that the
electron and MHD  fluid velocities are  discontinuous across the separatrix. (See Section~\ref{s8.6}.) As previously
mentioned, these discontinuities are resolved in a layer of characteristic thickness $\rho_\beta$.

We need to evaluate Equation~(\ref{e472}) to second order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
we obtain
\begin{equation}
0=\epsilon_d\,\{{\cal V}_1,{\mit\Omega}\} + \epsilon_\chi\,(X^2\,d_{\mit\Omega} {\cal V}_{(0)} + {\cal V}_{(0)}),
\end{equation}
where use has been made of Equations~(\ref{e498}) and (\ref{e508}). The flux-surface average of the
previous equation yields
\begin{equation}
\langle X^2\rangle\,d_{\mit\Omega} {\cal V}_{(0)} +\langle 1\rangle \,{\cal V}_{(0)}= 0.
\end{equation}
 The previous equation can be solved, subject to the boundary condition (\ref{e486a}) to
give
\begin{equation}
{\cal V}_{(0)}({\mit\Omega}, T) = 0.
\end{equation}
Hence, we conclude that the lowest-order ion parallel flow is unaffected by the presence of the island chain.

@@

Equations~(\ref{e528a}) and (\ref{e543}) can be combined to give (Fitzpatrick \& Waelbroeck 2005)
\begin{align}
{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) &=\frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\int_1^\infty
\left\langle X^{2}\,d_{\mit\Omega}\!\left[d_{\mit\Omega}(X^3\,d_{\mit\Omega}Y_i)\right]\right\rangle d{\mit\Omega}\nonumber\\[0.5ex]
&=\frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\int_1^\infty d_{\mit\Omega}\!\left(-\langle X\rangle\,Y_i
+2\,\langle X^3\rangle\,d_{\mit\Omega} Y_i + \langle X^5\rangle\,d_{\mit\Omega}^{\,2} Y_i\right)d{\mit\Omega}\nonumber\\[0.5ex]
&= \frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\,\lim_{\mit\Omega\rightarrow\infty}\left(-\langle X\rangle\,Y_i
+2\,\langle X^3\rangle\,d_{\mit\Omega} Y_i + \langle X^5\rangle\,d_{\mit\Omega}^{\,2} Y_i\right),
\end{align}
where use has been made of the facts that $Y_i$ is zero inside the island separatrix, and $Y_i$ is continuous across the separatrix.
Combining the previous equation with Equation~(\ref{e530}), we obtain (Fitzpatrick \& Waelbroeck 2005)
\begin{equation}\label{e545}
{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)  =- \frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi\,v'}{\hat{w}}.
\end{equation}
The previous equation yields
\begin{equation}
\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}} = \left(\frac{\tau_\varphi\,\hat{w}^{\,4}}{2\,\tau_H^{\,2}}\right){\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right),
\end{equation}
where use has been made of Equation~(\ref{e489}). The same relation can be obtained by integrating Equation~(\ref{e182}) across the resonant surface, making use of Equation~(\ref{e157}), as well as the
identification
\begin{equation}
\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}} = m\left[r\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right]_{r_{s-}}^{r_{s+}}.
\end{equation}
The previous identification  merely states that the  discontinuity in the MHD fluid velocity gradient that develop at the resonant
surface is mirrored by an equal discontinuity in the ion fluid velocity gradient (because the discontinuity is ultimately due to 
a discontinuity in the ${\bf E}\times {\bf B}$ velocity gradient).

@@

\section{Isolated Magnetic Island Chain}
\subsection{Introduction}
Suppose that the wall surrounding the plasma is perfectly conducting (i.e.\, $\tau_w\rightarrow\infty$), and that there is no current
flowing through the external magnetic-field coil (i.e., $\hat{I}_c=0$). In this case, assuming that $d/dt = -{\rm i}\,\omega$, Equations~(\ref{e202}), 
(\ref{e203}), and (\ref{epw}),  yield 
\begin{equation}\label{e563}
\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s} ={\mit\Delta}_{pw},
\end{equation}
where ${\mit\Delta}_{pw}$ is the (real) perfect-wall tearing stability index.

\subsection{Rutherford Island Width Evolution Equation}
It is clear from the previous equation that
\begin{equation}\label{e559}
{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) = 0,
\end{equation}
which implies that zero electromagnetic torque is exerted at the resonant surface. (See Section~\ref{storque}.) 
Moreover, 
\begin{equation}
{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) = {\mit\Delta}_{pw}.
\end{equation}
Hence, Equations~(\ref{e456}), (\ref{e559}), and (\ref{e559}) yield the {\em Rutherford island width evolution equation}\/ (Rutherford 1973):
\begin{equation}
I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)= {\mit\Delta}_{pw}.
\end{equation}
According to this equation, if the perfect-wall tearing stability index is positive then the width of the magnetic
island chain at the resonant surface grows algebraically on the resistive evolution timescale, $\tau_R$.
